Baseline centering problem

### 2018-11-25 paper/tangotd.tex

>>>>

Only $B=A^{-1}$ and $B=\transp{A}(A\transp{A})^{-1}$ are truly
second-order (namely, solve the problem in one step in the non-stochastic
case). The other algorithms involving an inverse basically have the cost
of second-order algorithms without the full benefits. They are
second-order in feature-space (they orthonormalize $\Phi$) but not in
Markov process space (they don't backpropagate rewards).
